---
title: "assignment8"
author: "aungmyatphyo"
date: "2022-10-07"
output: html_document
---
#1.1
```{r}
colon<- read.csv("colon_data.csv", header = T)
head(colon)
library(splines)
library(survival)
attach(colon)
list(colon$rx)
logrank1<-survdiff(Surv(colon$time,colon$status)~colon$rx)
logrank1
sfit1<-survfit(Surv(colon$time,colon$status)~colon$rx)
plot(sfit1, lty=c("solid","dashed"),col=c("blue","red"), xlab="survival times in days", ylab="survival probability")
title("Performance of the adjuvant therapy against placebo over duration of trial")
legend("topright", c("adjuvant therapy","placebo"),lty = c("solid","dashed"),col=c("blue","red"))
```
p-value is 1e-05 that rejects the null hypothesis.There is a significance difference between two groups(adjuvant therapy/placebo) in terms of survival.

##1.2
```{r}
obs<- colon[colon$rx=="Obs",]
obs
adj<- colon[colon$rx=="Lev+5FU",]
adj
```

```{r}
attach(obs)
logrank2<-survdiff(Surv(obs$time,obs$status)~obs$sex)
logrank2
sfit2<-survfit(Surv(obs$time,obs$status)~obs$sex)
plot(sfit2,lty = c("solid","dashed"),col=c("blue","red"),xlab="survival times in days", ylab="survival probability")
title("the effect of gender on survival within placebo")
legend("topright",c("female","male"),lty = c("solid","dashed"),col=c("blue","red"))
```
Within the placebo group,there is no significance difference between gender(male & female) in terms of survival because of p-value(0.8).

```{r}
attach(adj)
logrank3<-survdiff(Surv(adj$time,adj$status)~adj$sex)
logrank3
sfit3<-survfit(Surv(adj$time,adj$status)~adj$sex)
plot(sfit3,lty = c("solid","dashed"),col=c("blue","red"),xlab="survival times in days", ylab="survival probability")
title("the effect of gender on survival within treated cohorts")
legend("topright",c("female","male"),lty = c("solid","dashed"),col=c("blue","red"))
```
In the treated cohorts,there is a significance difference between male and female groups in terms of survival due to p-value,0.008.

##1.3
```{r}
attach(colon)
logrank4<-survdiff(Surv(colon$time,colon$status)~colon$node4)
logrank4
sfit4<-survfit(Surv(colon$time,colon$status)~colon$node4)
plot(sfit4, lty=c("solid","dashed"),col=c("blue","red"), xlab="survival times in days", ylab="survival probability")
title("impact having more than 4 positive lymphnodes")
legend("topright", c("more than 4 lymphnodes","less than 4"),lty = c("solid","dashed"),col=c("blue","red"))
```
p-value is 1e-13, so there is a significance difference between more than and less than 4 lymphnodes in terms of survival.

```{r}
attach(obs)
logrank5<-survdiff(Surv(obs$time,obs$status)~obs$node4)
logrank5
sfit5<-survfit(Surv(obs$time,obs$status)~obs$node4)
plot(sfit5,lty = c("solid","dashed"),col=c("blue","red"),xlab="survival times in days", ylab="survival probability")
title("the effect of having more than 4 positive lymphnodes on survival within placebo group")
legend("topright",c("more than 4","less than 4"),lty = c("solid","dashed"),col=c("blue","red"))
```
In placebo group, there is a significance difference between more than and less than 4 lymphnodes in terms of survival due to p-value,7e-07.

```{r}
attach(adj)
logrank6<-survdiff(Surv(adj$time,adj$status)~adj$node4)
logrank6
sfit6<-survfit(Surv(adj$time,adj$status)~adj$node4)
plot(sfit6,lty = c("solid","dashed"),col=c("blue","red"),xlab="survival times in days", ylab="survival probability")
title("the effect of having more than 4 positive lymphnodes on survival within treated cohorts")
legend("topright",c("more than 4","less than 4"),lty = c("solid","dashed"),col=c("blue","red"))
```
In treated with adjuvant therapy group, there is a significant effect between more than and less than 4 lymphnodes in terms of survival due to p-value(2e-08).

In survival based on gender, there is no significant difference in placebo group. However, there is significant different in adjuvant therapy group(males>females in survival).

In survival based on number of positive lymphnodes(more than & less than 4),there is a significant difference in not only placebo and therapy groups.

In conclusion, less than 4 positive lymphnodes is higher survival rate while male has higher survival rate in only adjuvant groups(male= female survival while placebo is prescribed).